\begin{acknowledgements}
I would like to thank my advisor, Warren Siegel, who has had to endure my stubbornness, ignorance and bad jokes. Warren has taught me many things, but he has also allowed me to learn many things on my own and at my own pace, and I am very thankful for that. I hope that other graduate advisors have the infinite amount of patience and sense of humor that Warren has.

My graduate committee: Peter van Nieuwenhuizen, Abhay Deshpande and Samuel Grushevsky. Thank you all for agreeing to be part of this. A special thanks to Peter, for allowing me to be his teaching assistant and to help with his lecture notes. It was my honor. Thank you for all the great lectures.

I thank professors Abanov, Likharev, Rastelli, Ro\v{c}ek, Stephens, Wang, Weinacht and Zahed for teaching me physics. A special thanks to professor Sterman for introducing me to QFT, for the informal discussions at his office, which always put me on a better path, and for indirectly showing me that the early morning is the best time of the day to think about path integrals.

But I could not have made it to Stony Brook without the lectures in Mayag\"{u}ez from professors Col\'{o}n, Chang, Jim\'{e}nez, L\'{o}pez, Marrero, M\'{e}ndez, Pab\'{o}n, Quintana, Roura and Vel\'{a}zquez. Gracias a ustedes, pude.

The Center for Inclusive Education has supported me both financially and emotionally. I thank all the staff, the students and the director, Nina Maung-Gaona. Your support was crucial. It was an honor to be a Turner Fellow.

My peers in Stony Brook: Dharmesh, Ozan, Marcos, and others at the YITP; Abhijit, Stephen and the class of 2006; Eitan, for the math seminars and rides to campus, and Glenn for being a mentor. My older brothers-in-Siegel: Peng Dai and Yu-Tin Huang, for all the help and support. But I found true siblings in Pedro and Pilar: thank you for welcoming me at your house and at your lunch table, for listening, for caring and for advising.

My family and friends in Puerto Rico, California, Texas, New Jersey and elsewhere: without your support and encouragement it would have been impossible. Thank you for always being there.

And my wife, Merideth. Thank you for being so amazing and loving. I am glad I have you near. Please, stop baking cookies; you are making me fat. ${\color{blue} \heartsuit}$
\end{acknowledgements}